---
title: "Viral Map Tracker"
author: "Elias Ciudad"
date: "2025-03-17"
output: html_document
runtime: shiny
---



```{r setup, include=FALSE}
#sknitr::opts_chunk$set(echo = TRUE)
source("D:/Academical Things/Programming/R/Workspaces/Virus_Outbreak_Tracking_Tool/bin/R/confirmed_cases/libraries.R")
```


```{r data processing}
source("D:/Academical Things/Programming/R/Workspaces/Virus_Outbreak_Tracking_Tool/bin/R/confirmed_cases/data_processing.R")
```

## Inputs and Outputs
You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
ui <- fluidPage(
  titlePanel("Viral Outbreak Tracking Tool"),
  
  sidebarLayout(
    sidebarPanel(
      #selectInput("dataset", "Select a dataset:", choices = c("Physicians", "Nurses")),
      #selectInput("county", "Select a county/city:", choices = unique(bexar_county_medical_licenses_sf$practice_county))
    ),
    mainPanel(
      tabsetPanel(
        #tabPanel("Map", leafletOutput("map")),
        #tabPanel("Age Distribution", plotOutput("zipcode_age_plot")),
        #tabPanel("License Type", plotOutput("zipcode_license_plot"))
      )
    )
  )
)
```

## Embedded Application
It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
server <- function(input, output) {}
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.

```{r}
shinyApp(ui, server)
```


